Freezing of a Weeks-Chandler-Anderson Fluid using classical Density Functional Theory

### 2020-11-07 papers/thesis-kirstie/thesis.tex
edits

The result can be made more accurate by increasing NumPoints (the 
number of vectors randomly generated), and by using antithetic variates.
%
 \begin{figure}[h!]
    \centering
    %\includegraphics[height=6cm]{GaussandW2_actual.png}
    \includegraphics[height=7cm]{weightandGuass1.pdf}
    %\caption{A Gaussian centered at $\vec{R}$ is shown in blue, and a cross-sectional 
    %view of $w_2$ centered at $\vec{r}'$ is shown in purple.} 
    \caption{A Gaussian distribution about a lattice site located at 
    $\vec R$ is shown in blue, and a cross-sectional 
    view of $w_2$ centered at $\vec{r}'$ is shown in purple.} 
    %Here, the weight function 
    %is evaluated at $\vec{r}-\vec{r}'$ where $\vec{r}'=\vec{R}+\vec{dr}$ and $\vec{dr}$ 
    %is generated randomly according to a Gaussian distribution.} 
  \label{fig:GaussandW2_actual}
  \end{figure} 
%
 \begin{figure}[h!]
    \centering
    %\includegraphics[height=6cm]{GaussandW2_thinkas.png}
    \includegraphics[height=7cm]{weightandGuass2.pdf}
    \caption{An alternative way of viewing Figure~\ref{fig:GaussandW2_actual} where 
    the weight function, shown by the purple dashed lines, is centered at $\vec{r}$,  
    and fixed in place as $\vec r' - \vec R$
    %as $\vec{dr}=\vec{r}'-\vec{R}$ 
    varies randomly with a probability according to a Gaussian distribution.} 
  \label{fig:GaussandW2_thinkas}
  \end{figure} 
%
%Monte-Carlo integration is employed to more efficiently 
%compute the weighted densities used to calculate the excess free energy which is then 
%added to the ideal free energy (computed analytically) to get the total free energy 
%which is minimized. 
%
%-------Antithetic-------------------
%To further reduce the error in the average, antithetic variates are used. 
%Rather than computing an average of a set of random points, 
%antithetic variates can be used to reduce error. 
To use antithetic variates,
each randomly generated  vector is paired with a 
vector of equal magnitude, but opposite in direction. 
%as shown in Figure \ref{fig:AntitheticVariate}. 
%The quantity that is a function of the randomly generated vector
%now has two values that can be averaged to get a more accurate value. 
First order error is reduced
%in the quantity that is a function of the randomly generated vector
%average by filtering out an erroneous offset of values 
%along the line connecting the two points 
by averaging the two results, one of 
which may be erroneously higher than it should be while the other is 
erronesously lower than it should be.

>>>>

The result can be made more accurate by increasing NumPoints (the 
number of vectors randomly generated), and by using antithetic variates.
%
 \begin{figure}[h!]
    \centering
    %\includegraphics[height=6cm]{GaussandW2_actual.png}
    \includegraphics[height=7cm]{weightandGuass1.pdf}
    %\caption{A Gaussian centered at $\vec{R}$ is shown in blue, and a cross-sectional 
    %view of $w_2$ centered at $\vec{r}'$ is shown in purple.} 
    \caption{A Gaussian distribution about a lattice site located at 
    $\vec R$ is shown in blue, and a cross-sectional 
    view of $w_2$ centered at $\vec{r}'$ is shown in purple.} 
    %Here, the weight function 
    %is evaluated at $\vec{r}-\vec{r}'$ where $\vec{r}'=\vec{R}+\vec{dr}$ and $\vec{dr}$ 
    %is generated randomly according to a Gaussian distribution.} 
  \label{fig:GaussandW2_actual}
  \end{figure} 
%
 \begin{figure}[h!]
    \centering
    %\includegraphics[height=6cm]{GaussandW2_thinkas.png}
    \includegraphics[height=7cm]{weightandGuass2.pdf}
    \caption{An alternative way of viewing Figure~\ref{fig:GaussandW2_actual} where 
    the weight function, shown by the purple dashed lines, is centered at $\vec{r}$,  
    and fixed in place as $\vec r' - \vec R$
    %as $\vec{dr}=\vec{r}'-\vec{R}$ 
    varies randomly with a probability according to a Gaussian distribution.} 
  \label{fig:GaussandW2_thinkas}
  \end{figure} 
%
%Monte-Carlo integration is employed to more efficiently 
%compute the weighted densities used to calculate the excess free energy which is then 
%added to the ideal free energy (computed analytically) to get the total free energy 
%which is minimized. 
%
%-------Antithetic-------------------
%To further reduce the error in the average, antithetic variates are used. 
%Rather than computing an average of a set of random points, 
%antithetic variates can be used to reduce error. 
To use antithetic variates,
each randomly generated  vector is paired with a 
vector of equal magnitude, but opposite in direction. 
%as shown in Figure \ref{fig:AntitheticVariate}. 
%The quantity that is a function of the randomly generated vector
%now has two values that can be averaged to get a more accurate value. 
First order error is reduced
%in the quantity that is a function of the randomly generated vector
%average by filtering out an erroneous offset of values 
%along the line connecting the two points 
by averaging the two results that depend on the vectors, one of 
which may be erroneously higher than it should be while the other is 
erronesously lower than it should be.
